 %!TEX root = main.tex

The baseline MIP was solved to global optimality using FICO~Xpress imported as a
Python library with a time limit of 300~seconds.
The solver terminates in less than 0.1~second ($0.026$~s), confirming the
tractability of the model and the suitability of the chosen formulation for the
given instance.

\paragraph{Optimal configuration.}
The solver opens 14 out of 15 warehouses; only warehouse~W9 (Sydney) remains
closed.
Sydney is connected to five hubs and one neighbouring warehouse~(W15~Bangalore),
yet serves a single customer, C26~(Sapporo, Japan), already well covered by
closer Asia-Pacific facilities, making its \$1{,}366 opening cost impossible to
justify.
Of the 47 optional arcs, 11 are activated; all are road connections providing
last-mile delivery from warehouses to nearby customers (arcs A225, A235, A242,
A261, A278, A285, A288, A291, A294, A309, A315).
The optimal cost decomposes as shown in Table~\ref{tab:phase1costs}.

\begin{table}[H]
\centering
\caption{Baseline cost decomposition.}
\label{tab:phase1costs}
{\footnotesize\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Component} & \textbf{Cost (\$)} & \textbf{Share} \\
\midrule
Warehouse opening     &      22{,}046 &  0.5\% \\
Arc activation        &      19{,}638 &  0.5\% \\
Transport --- A (Fert.) &    638{,}198 & 14.3\% \\
Transport --- B (Semi.) &  2{,}814{,}741 & 63.2\% \\
Transport --- C (Batt.) &    960{,}176 & 21.6\% \\
\midrule
\textbf{Total} $Z^*$  & \textbf{4{,}454{,}801} & 100\% \\
\bottomrule
\end{tabular}}
\end{table}

\paragraph{Network structure.}
Hub load is highly asymmetric.
Singapore~(H3) is the dominant transit node: it routes \emph{all} 2{,}222~units
of semiconductor demand, 100\% of product~B supply,plus 631~units of
battery components, for a combined throughput of 2{,}853~units.
This concentration creates the network's central single point of failure,
discussed further in Phase~2.
Frankfurt~(H1) is the primary hub for fertilisers~(A), handling 1{,}050~units
(50\% of~A demand), while Dubai~(H2) is the only hub active for all three
products simultaneously (338~A, 722~B, 631~C).
Chicago~(H4) and S\~ao Paulo~(H5) serve regional spill-over demand and carry
693 and 1{,}168~units respectively; H5 routes only fertilisers~(A) and battery
components~(C), while H4 handles 536~units of semiconductor~(B) relayed through
W6, which itself draws entirely from H3, so H4 inherits indirect exposure to
the H3 single-point-of-failure.

Warehouse utilisation spans a wide range: Rotterdam~(W1) operates at
91.3\%~capacity, while Chennai~(W5) reaches only 4.1\%.
Despite this under-utilisation, W5 remains open because it provides the sole
feasible last-mile connection for one South Indian customer (arc~A315) whose
demand cannot be rerouted without activating a more expensive path.
The three European warehouses~(W1--W3) together absorb most of fertiliser
outflow, consistent with the agricultural-demand concentration in that region.

The cost-minimising solution  uses sea transport for long-haul legs and road for 
last-mile delivery. 
Sea freight accounts for 74--82\% of flow volume across all three products;
road handles the remaining 18--26\% exclusively in warehouse-to-customer arcs.

\subsection*{Formulation Quality and LP~Relaxation}

\paragraph{Aggregated vs.\ disaggregated capacity constraints.}
Our formulation uses \emph{aggregated} arc-capacity constraints~(C4):
\[
  \sum_{p \in P} x_a^p \;\leq\; \mathit{CapArc}_a \cdot z_a
  \qquad \forall\, a \in A_{\text{fixed}},
\]
An alternative \emph{disaggregated} formulation imposes one
constraint per product:
\[
  x_a^p \;\leq\; \mathit{CapArc}_a \cdot z_a
  \qquad \forall\, p \in P,\; a \in A_{\text{fixed}},
\]
adding $|P| \cdot |A_{\text{fixed}}| = 141$ constraints instead
of~47.
Disaggregated constraints are theoretically tighter when each
product has its own dedicated capacity. Here, however, arc
capacities are \emph{shared} across all products simultaneously:
the disaggregated formulation bounds each product's flow
individually against the full arc capacity, implicitly allowing
their sum to exceed it in the LP relaxation.
Empirically, the disaggregated LP yields
$Z_{\text{LP}}^* = \$4{,}421{,}640$ (gap $0.744\%$), a
\emph{weaker} bound than the aggregated version by \$3{,}003.
The aggregated constraint~(C4) is therefore the tighter and more
natural formulation for this shared-capacity network.
We retain it for both correctness and simplicity.

\subsection*{Network Vulnerability: Min-Cut Analysis}

\paragraph{Global min-cut.}
To characterise the structural robustness of the baseline network,
we compute the global min-cut using a max-flow formulation with a
super-source connected to all suppliers and a super-sink connected
to all customers. The global min-cut value equals \textbf{6,197
units}, which coincides exactly with total demand (bottleneck
ratio: 100\%). The saturated cut passes entirely through the
demand arcs (customer $\rightarrow$ super-sink), confirming that
no internal arc capacity is the binding constraint under baseline
conditions, the network is dimensioned precisely to meet demand
without slack.

\paragraph{Node criticality.}
We assess node criticality by computing the max-flow achievable
after removing each node individually.
Table~\ref{tab:node_criticality} reports the results for the
four critical nodes identified.

\begin{table}[H]
\centering
\caption{Node criticality: flow loss upon node removal.}
\label{tab:node_criticality}
\small
\begin{tabular}{llrr}
\toprule
\textbf{Node} & \textbf{Type} & \textbf{Flow drop} & \textbf{\%} \\
\midrule
H3 (Singapore)  & Hub & 2{,}853 & 46.0\% \\
H1 (Frankfurt)  & Hub &   973   & 15.7\% \\
H2 (Dubai)      & Hub &   887   & 14.3\% \\
H5 (São Paulo)  & Hub &   828   & 13.4\% \\
\bottomrule
\end{tabular}
\end{table}

Hub~H3 (Singapore) is by far the most critical node: its removal
causes a 46\% collapse in network throughput, far exceeding the
impact of any other node. This structural dependency directly
anticipates the infeasibility of Scenarios~S1 and~S3 in Phase~2,
where H3 closure strands suppliers~S6 and~S9 with no alternative
routing path. The remaining active hubs (H1~Frankfurt, H2~Dubai,
H5~São Paulo) each account for 13--16\% of throughput; their
geographic dispersion across Europe, the Middle East, and the
Americas provides partial resilience against single-region hub
disruptions, but no substitute for H3's role in the Asia-Pacific
corridor.

At the warehouse layer, no individual facility removal degrades
throughput, confirming that warehouse placement serves
cost-optimisation rather than feasibility. However, a
combinatorial analysis reveals a collective vulnerability: removing
as few as two warehouses simultaneously can reduce flow by 7.3\%
(Rotterdam and Madrid), and three Americas-cluster warehouses
(Houston, Toronto, Monterrey) together cut throughput by 14.5\%.
The threshold for a \textgreater{}20\% degradation is reached at
$k = 4$ simultaneous closures, all concentrated in the Americas
region. This correlated regional fragility is directly relevant to
the canal disruption scenarios in Phase~3: Panama Canal capacity
reductions simultaneously constrain multiple arcs serving these
same Americas warehouses, effectively replicating a correlated
regional shock on the warehouse layer.

\begin{tcolorbox}[notebox, title={Phase~1 key finding}]
\small
The cost-minimising network concentrates 100\% of semiconductor supply
through a single hub~(H3, Singapore).
This structural dependency is cost-optimal under normal conditions but
creates a critical single point of failure under supply-disruption scenarios.
\end{tcolorbox}
