 %!TEX root = main.tex

 \subsection{Response Strategy Framework}

For each adverse scenario, three response strategies are evaluated:

\begin{itemize}[leftmargin=*,itemsep=2pt]
  \item \textbf{R : Rerouting only.} The baseline infrastructure
    ($W^*, A^*$) is held fixed; only flow routing is re-optimised.
    Fixed costs are sunk and not re-incurred. This represents the
    immediate, operational response horizon.

  \item \textbf{A : Adaptation.} Warehouse opening and arc activation
    decisions are freed; the solver may open or close facilities and
    activate or deactivate arcs at their respective costs. This represents
    a medium-term reconfiguration.

  \item \textbf{F : Full redesign.} Phase~1 is re-solved from scratch under
    the scenario's parameters, ignoring sunk costs. This gives a lower bound
    on achievable cost and represents the long-run strategic horizon.
\end{itemize}

The disruption cost for a given scenario~$s$ and strategy~$\sigma$ is:
\begin{equation}
  \Delta Z(s,\sigma) = Z(s,\sigma) - Z^*
  \label{eq:deltaz}
\end{equation}
where $Z^*$ is the baseline optimal cost from Phase~1.

\subsection{Scenario Overview}

Table~\ref{tab:scenarios} summarises the six scenarios.

\begin{table}[H]
\centering
\caption{Phase~2 adversarial scenarios.}
\label{tab:scenarios}
\begin{tabular}{lll}
\toprule
\textbf{ID} & \textbf{Type} & \textbf{Shock} \\
\midrule
T1 & Tariff      & $+40\%$ transatlantic/transpacific \\
T2 & Energy      & Air $+60\%$, road $+20\%$, sea $+10\%$ \\
T3 & Seasonal    & Hub handling fees $+30\%$ (Q4) \\
S1 & Node loss   & H3 (Singapore) closed \\
S2 & Arc loss    & Korea--Europe corridor blocked \\
S3 & Combined    & T2 $+$ S1 simultaneously \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{T1 : Trump-era tariff shock.}
A 40\% surcharge is applied to all arcs crossing the transatlantic and
transpacific corridors, primarily affecting products~B and~C whose supply
chains rely heavily on Asia--Americas and Asia--Europe routes.
Under strategy~R, flows can be partially rerouted through Middle East or
intra-regional corridors; under~F, the network may reorganise around
lower-tariff paths.

\paragraph{T2 : Energy crisis.}
Inspired by the Ukraine/Iran conflict, this scenario raises air freight by
60\%, road by 20\%, and sea by 10\%. The asymmetric impact penalises
time-sensitive, air-intensive routing heavily. Products with modal
flexibility benefit most from adaptation.

\paragraph{T3 : Seasonal hub surcharge.}
A 30\% surcharge on hub handling fees during Q4 raises the effective cost
of all hub-transiting flows. Products that route through multiple hubs
(notably~A via sea and~B via air) are most exposed.

\paragraph{S2 : Korea--Europe corridor blockade.}
A set of arcs representing the South Korea export corridor to Europe are
removed. This primarily disrupts product~B (semiconductors), which relies
on Korean-origin flows. Alternative routing through other hubs is feasible,
at higher cost.

\subsection{S1 and S3: Structural Infeasibility and Modified Formulation}
\label{sec:s1s3}

Scenarios S1 and~S3 involve the closure of hub~H3 (Singapore), motivated
by a simulated Taiwan Strait crisis. Unlike the other scenarios, these
are \emph{structurally infeasible} under the standard formulation
(equations \ref{eq:C1}--\ref{eq:C8}).

\paragraph{Root cause.}
Suppliers S4, S5, and~S6 (producing product~B) and supplier~S9
(producing product~C) are exclusively connected to the network through~H3.
When H3 is removed, all 42 arcs incident to it are severed, leaving
these suppliers with no outgoing path. The resulting supply deficit is:

\begin{itemize}[leftmargin=*,itemsep=1pt]
  \item Product~B: $-2{,}223$ units (100\% of total supply stranded)
  \item Product~C: $-631$ units (33\% of total supply stranded)
\end{itemize}

With C1 as a hard equality constraint, no feasible solution exists.

\paragraph{Modified formulation for strategies R and A.}
We introduce a non-negative slack variable $unmet_c^p \in [0, Dem_c^p]$
representing unserved demand, and replace~\eqref{eq:C1} with:
\begin{equation}
  \sum_{a \in S_{\text{target}}^c} x_a^p + unmet_c^p = Dem_c^p
  \quad \forall\, p \in P,\; c \in C
  \label{eq:C1_relaxed}
\end{equation}
The objective gains a penalty term $M \cdot \sum_{c,p} unmet_c^p$ with
$M = 10^6$, large enough to ensure unmet demand is never preferred over
any feasible routing. The logistics cost reported excludes the penalty:
$Z_{\text{logistics}} = Z_{\text{obj}} - M \cdot \sum_{c,p} unmet_c^p$.

\paragraph{Modified formulation for strategy F.}
Full demand satisfaction
is restored by injecting one emergency supply arc per
stranded supplier, connecting it to the geographically
closest remaining active hub. The unit cost scales with
distance: $c_a^{\text{emg},p} = \gamma \cdot \hat{c}^{s,p}
\cdot \hat{d}^{s,h}$, where $\hat{c}^{s,p}$ is the
cost-per-km derived from the supplier's original baseline
arc, $\hat{d}^{s,h}$ is the estimated rerouting distance
via the removed hub, and $\gamma = 2.5$ models spot-market
procurement. Under~F, constraint~\eqref{eq:C1} is enforced
as a hard equality, the emergency arcs restore
feasibility while the objective captures the full
procurement premium.

\subsection{Phase 2 Results}
\label{sec:phase2_results}

Table~\ref{tab:phase2_results} summarises the logistics cost
$Z_{\text{log}}$ delivered by each strategy across the six scenarios,
together with the disruption cost $\Delta Z_F$ achieved by the
greenfield benchmark. All values reported here are
\emph{logistics costs} (sunk + new fixed + variable), excluding the
penalty term $M \cdot \mathit{unmet}$, they are therefore directly
comparable to $Z^* = \$4{,}454{,}801$ from Phase~1.

\begin{table}[H]
\centering
\caption{Phase~2 logistics costs (\$). $\Delta Z_F = Z_F - Z^*$.}
\label{tab:phase2_results}
\small
\setlength{\tabcolsep}{3pt}
\begin{tabular}{lrrrrrl}
\toprule
\textbf{Sc.} & $Z_R$ & $Z_A$ & $Z_F$ & $\Delta Z_F$ & $\Delta\%$ & \textbf{Best} \\
\midrule
T1 & 4{,}610{,}797 & 4{,}610{,}341 & 4{,}610{,}256 &   155{,}456 &   3.49 & F \\
T2 & 4{,}928{,}846 & 4{,}928{,}846 & 4{,}928{,}846 &   474{,}045 &  10.64 & R \\
T3 & 5{,}406{,}145 & 5{,}307{,}901 & 5{,}307{,}084 &   852{,}284 &  19.13 & F \\
S1$^\dagger$ & 1{,}343{,}415 & 1{,}344{,}313 & 8{,}088{,}281 & 3{,}633{,}480 &  81.56 & F \\
S2 & 4{,}454{,}801 & 4{,}454{,}801 & 4{,}454{,}801 &           0 &   0.00 & --- \\
S3$^\dagger$ & 1{,}493{,}239 & 1{,}494{,}105 & 8{,}443{,}935 & 3{,}989{,}134 &  89.55 & F \\
\bottomrule
\end{tabular}\\
\footnotesize
$^\dagger$ Under S1 and~S3, strategies R and A leave $2{,}853$ units
of demand unserved (B: $2{,}222$, C: $631$). Their reported
$Z_R, Z_A$ exclude the penalty $M\cdot\mathit{unmet}$ and are
therefore not comparable to $Z_F$ or to $Z^*$.
\end{table}

\paragraph{Monotonicity check.}
For every \emph{feasible} scenario the expected ordering
$Z_F \leq Z_A \leq Z_R$ is respected: in T1, T3 the inequalities are
strict; in T2 and~S2 the three strategies tie because the baseline
network already supports the optimal flow under the shock and no
reconfiguration is value-creating. For the infeasible scenarios
(S1, S3) the ordering is inverted on the logistics-cost ledger
($Z_R < Z_A \ll Z_F$) precisely because R and A leave most of the
flow unserved, see the dedicated discussion below.

\subsubsection*{Feasible scenarios (T1, T2, T3, S2)}

\paragraph{T1 : Transatlantic/transpacific tariff.}
The $+40\%$ surcharge on cross-Pacific and cross-Atlantic arcs is
absorbed almost entirely at the variable-cost layer: the network
structure is not strained, only its operating cost. Strategy~F yields
$Z_F = \$4{,}610{,}256$ ($\Delta Z = +\$155{,}456$, $+3.49\%$),
of which $\$22{,}046$ are warehouse opening costs, $\$21{,}222$ are
arc activation costs, and $\$4{,}566{,}988$ are variable transport
costs. The flexibility value $Z_R - Z_A = \$456$ is negligible:
strategy~A buys the network only the right to activate two extra
arcs (A188: W1$\rightarrow$W12 sea; A224: W12$\rightarrow$C1 road)
that shave less than one part in ten thousand off the rerouting bill.
Economically, T1 is a \emph{pure price shock}, the baseline topology
is already near-optimal and there is nothing structural for
adaptation to fix.

\begin{table}[H]
\centering
\caption{Cost decomposition --- scenario T1 (\$).}
\label{tab:cost_decomp_t1}
\resizebox{\linewidth}{!}{%
\begin{tabular}{lrrrr}
\toprule
\textbf{Component} & \textbf{Baseline} & \textbf{R} & \textbf{A} & \textbf{F} \\
\midrule
\multicolumn{5}{l}{\textit{Fixed costs}} \\
~~WH opening (sunk) & \$22,046 & \$22,046 & \$22,046 & \$0 \\
~~WH opening (new) & \$0 & \$0 & \$0 & \$22,046 \\
~~Arc activation (sunk) & \$19,638 & \$19,638 & \$19,638 & \$0 \\
~~Arc activation (new) & \$0 & \$0 & \$2,400 & \$21,222 \\
\midrule
\multicolumn{5}{l}{\textit{Variable transport costs by product}} \\
~~A (Fertilizers) & \$638,198 & \$683,913 & \$681,599 & \$681,599 \\
~~B (Semiconductors) & \$2,814,741 & \$2,911,860 & \$2,911,316 & \$2,911,316 \\
~~C (Battery Comp.) & \$960,176 & \$973,340 & \$973,341 & \$974,072 \\
\midrule
\textbf{Total $Z$} & \$4,454,801 & \$4,610,797 & \$4,610,341 & \$4,610,256 \\
\midrule
$\Delta Z$ vs $Z^*$ & --- & \$+155,997 & \$+155,541 & \$+155,456 \\
$\Delta Z$ (\%) & --- & +3.5\% & +3.5\% & +3.5\% \\
Flex.\ value $Z_R - Z_A$ & --- & \multicolumn{2}{c}{\$456} & --- \\
\bottomrule
\end{tabular}%
}
\end{table}

\begin{table}[H]
\centering
\caption{Network changes vs.\ baseline --- scenario T1.}
\label{tab:network_t1}
\resizebox{\linewidth}{!}{%
\begin{tabular}{llllr}
\toprule
\textbf{Strategy} & \textbf{Arc} & \textbf{Route} & \textbf{Mode} & \textbf{Fixed cost (\$)} \\
\midrule
R & \multicolumn{4}{l}{No change vs.\ baseline} \\
\midrule
A & A188 & W1$\to$W12 & sea & \$683 \\
 & A224 & W12$\to$C1 & road & \$1,718 \\
\midrule
F & A188 & W1$\to$W12 & sea & \$683 \\
 & A224 & W12$\to$C1 & road & \$1,718 \\
 & A225 & W11$\to$C1 & road & (deactivated) \\
\midrule
\bottomrule
\end{tabular}
}
\end{table}
 



\paragraph{T2 : Energy crisis.}
The asymmetric modal surcharge (air $+60\%$, road $+20\%$, sea $+10\%$)
lifts every strategy to exactly $Z_F = \$4{,}928{,}846$
($+10.64\%$): R, A and F coincide. The baseline already routes
flows along the cheapest modal mix for the products it carries, and
no warehouse reconfiguration, arc activation, or full redesign can
improve on it under a uniform per-mode multiplier, every alternative
path is penalised at least as much as the current one. The
flexibility value collapses to zero. The disruption cost is therefore
a \emph{floor}: any network operating these products under this
modal mix will pay $+10.64\%$. This conclusion aligns with the Phase~1 network design: the majority of freight is 
routed via sea, which experiences the smallest cost increase in this scenario.

\begin{table}[H]
\centering
\caption{Cost decomposition --- scenario T2 (\$).}
\label{tab:cost_decomp_t2}
\resizebox{\linewidth}{!}{%
\begin{tabular}{lrr}
\toprule
\textbf{Component} & \textbf{Baseline} & \textbf{R, A, F} \\
\midrule
\multicolumn{3}{l}{\textit{Fixed costs}} \\
~~WH opening (sunk) & \$22,046 & \$22,046 \\
~~WH opening (new) & \$0 & \$0 \\
~~Arc activation (sunk) & \$19,638 & \$19,638 \\
~~Arc activation (new) & \$0 & \$0 \\
\midrule
\multicolumn{3}{l}{\textit{Variable transport costs by product}} \\
~~A (Fertilizers) & \$638,198 & \$714,724 \\
~~B (Semiconductors) & \$2,814,741 & \$3,107,930 \\
~~C (Battery Comp.) & \$960,176 & \$1,064,507 \\
\midrule
\textbf{Total $Z$} & \$4,454,801 & \$4,928,846 \\
\midrule
$\Delta Z$ vs $Z^*$ & --- & \$+474,045 \\
$\Delta Z$ (\%) & --- & +10.6\% \\
Flex.\ value $Z_R - Z_A$ & --- & \$0 \\
\bottomrule
\end{tabular}
}
\end{table}


\begin{table}[H]
\centering
\caption{Significant flow shifts under R --- scenario T2 (arcs with $|\Delta \text{flow}| > 10$ units).}
\label{tab:r_shifts_t2}
\resizebox{\linewidth}{!}{%
\begin{tabular}{llrrrr}
\toprule
\textbf{Arc} & \textbf{Product} & \textbf{Flow (BL)} & \textbf{Flow (R)} & $\Delta$\textbf{Flow} & $\Delta$\textbf{Cost (\$)} \\
\midrule
A133 (W6$\to$H4) & B (Semiconductors) & 453 & 536 & +83 & +184,278 \\
A120 (H3$\to$W15) & B (Semiconductors) & 157 & 463 & +306 & +83,105 \\
A102 (H3$\to$W6) & B (Semiconductors) & 660 & 743 & +83 & +61,516 \\
A013 (H2$\to$H1) & B (Semiconductors) & 352 & 403 & +51 & +43,844 \\
A066 (H2$\to$W3) & B (Semiconductors) & 146 & 213 & +67 & +31,944 \\
A069 (W4$\to$H2) & B (Semiconductors) & 243 & 310 & +67 & +17,775 \\
A142 (H4$\to$W11) & B (Semiconductors) & 352 & 435 & +83 & +7,021 \\
A002 (S1$\to$H2) & A (Fertilizers) & 325 & 338 & +13 & +6,416 \\
A062 (H2$\to$W1) & C (Battery Comp.) & 223 & 206 & -17 & +4,393 \\
A068 (H2$\to$W4) & A (Fertilizers) & 195 & 208 & +13 & +3,009 \\
A001 (S1$\to$H1) & A (Fertilizers) & 369 & 356 & -13 & +1,129 \\
A042 (H1$\to$W6) & A (Fertilizers) & 44 & 31 & -13 & -2,170 \\
A066 (H2$\to$W3) & C (Battery Comp.) & 280 & 217 & -63 & -5,711 \\
\bottomrule
\end{tabular}
}
\end{table}


\paragraph{T3 : Q4 hub surcharge.}
The $+30\%$ handling-fee shock is the most interesting feasible
case. Strategy~R is stuck with $Z_R = \$5{,}406{,}145$ ($+21.36\%$),
but adaptation activates 10~optional arcs at a fixed-cost premium of
only $\$12{,}297$, cutting variable cost by $\$110{,}540$ and
landing at $Z_A = \$5{,}307{,}901$ ($+19.15\%$). The greenfield
benchmark $Z_F = \$5{,}307{,}084$ ($+19.13\%$) improves on A by a
further $\$817$ only, adaptation captures $99.2\%$ of the
greenfield benefit. T3 is the only feasible scenario in which the
\emph{flexibility value} $Z_R - Z_A = \$98{,}244$ is economically
meaningful: when hub-handling costs rise across the board, the
solver gains by bypassing congested hub corridors via
direct warehouse-to-warehouse links such as A185 (W3$\rightarrow$W1),
A199 (W4$\rightarrow$W3 sea) and A317 (W4$\rightarrow$C30). The
ten activated arcs are the operationally most valuable
``insurance'' arcs in the entire scenario library. Since the fixed cost of pre-activating all ten arcs (\$12{,}297) 
is negligible relative to the flexibility value they unlock 
(\$98{,}244), these arcs are strong candidates for inclusion in 
the baseline network design as a low-cost seasonal hedge.
\begin{table}[H]
\centering
\caption{Cost decomposition --- scenario T3 (\$).}
\label{tab:cost_decomp_t3}
\resizebox{\linewidth}{!}{%
\begin{tabular}{lrrrr}
\toprule
\textbf{Component} & \textbf{Baseline} & \textbf{R} & \textbf{A} & \textbf{F} \\
\midrule
\multicolumn{5}{l}{\textit{Fixed costs}} \\
~~WH opening (sunk) & \$22,046 & \$22,046 & \$22,046 & \$0 \\
~~WH opening (new) & \$0 & \$0 & \$0 & \$22,046 \\
~~Arc activation (sunk) & \$19,638 & \$19,638 & \$19,638 & \$0 \\
~~Arc activation (new) & \$0 & \$0 & \$12,297 & \$31,119 \\
\midrule
\multicolumn{5}{l}{\textit{Variable transport costs by product}} \\
~~A (Fertilizers) & \$638,198 & \$760,627 & \$742,314 & \$742,314 \\
~~B (Semiconductors) & \$2,814,741 & \$3,407,734 & \$3,317,083 & \$3,317,083 \\
~~C (Battery Comp.) & \$960,176 & \$1,196,099 & \$1,194,522 & \$1,194,522 \\
\midrule
\textbf{Total $Z$} & \$4,454,801 & \$5,406,145 & \$5,307,901 & \$5,307,084 \\
\midrule
$\Delta Z$ vs $Z^*$ & --- & \$+951,344 & \$+853,101 & \$+852,284 \\
$\Delta Z$ (\%) & --- & +21.4\% & +19.2\% & +19.1\% \\
Flex.\ value $Z_R - Z_A$ & --- & \multicolumn{2}{c}{\$98,244} & --- \\
\bottomrule
\end{tabular}
}
\end{table}
\vspace{0pt}
\begin{table}[H]
\centering
\caption{Network changes vs.\ baseline --- scenario T3.}
\label{tab:network_t3}
\resizebox{\linewidth}{!}{%
\begin{tabular}{llllr}
\toprule
\textbf{Strategy} & \textbf{Arc} & \textbf{Route} & \textbf{Mode} & \textbf{Fixed cost (\$)} \\
\midrule
R & \multicolumn{4}{l}{No change vs.\ baseline} \\
\midrule
A & A185 & W3$\to$W1 & road & \$661 \\
 & A188 & W1$\to$W12 & sea & \$683 \\
 & A190 & W1$\to$W14 & sea & \$1,650 \\
 & A199 & W4$\to$W3 & sea & \$1,671 \\
 & A210 & W5$\to$W15 & road & \$1,147 \\
 & A223 & W14$\to$W12 & sea & \$743 \\
 & A224 & W12$\to$C1 & road & \$1,718 \\
 & A241 & W2$\to$C5 & sea & \$2,228 \\
 & A251 & W2$\to$C9 & road & \$797 \\
 & A317 & W4$\to$C30 & road & \$1,000 \\
\midrule
F & A185 & W3$\to$W1 & road & \$661 \\
 & A188 & W1$\to$W12 & sea & \$683 \\
 & A190 & W1$\to$W14 & sea & \$1,650 \\
 & A199 & W4$\to$W3 & sea & \$1,671 \\
 & A210 & W5$\to$W15 & road & \$1,147 \\
 & A223 & W14$\to$W12 & sea & \$743 \\
 & A224 & W12$\to$C1 & road & \$1,718 \\
 & A241 & W2$\to$C5 & sea & \$2,228 \\
 & A251 & W2$\to$C9 & road & \$797 \\
 & A317 & W4$\to$C30 & road & \$1,000 \\
 & A225 & W11$\to$C1 & road & (deactivated) \\
\midrule
\bottomrule
\end{tabular}
}
\end{table}
\vspace{0pt}
\paragraph{S2 : Korea--Europe corridor.}
The blocked arcs are simply not part of the baseline optimal flow:
$Z_R = Z_A = Z_F = Z^*$, $\Delta Z = 0$. The corridor was a feasible
but inactive option in Phase~1 and its removal has no economic effect.
This is a useful negative result: not every shock translates into a
disruption.


\subsubsection*{Infeasible scenarios (S1, S3)}

\paragraph{Reading the table for S1 and S3.}
Suppliers~S4, S5, S6 (semiconductors) and~S9 (battery components)
connect to the network exclusively through hub~H3. Removing H3 leaves
$2{,}222$ units of~B and $631$ units of~C with no outgoing path
under strategies R and~A. The corresponding logistics cost
($Z_R \approx \$1{,}343{,}415$ for S1, $Z_R \approx \$1{,}493{,}239$
for S3) is \emph{cheaper than the baseline} only because two thirds
of $B$ and one third of~$C$ are simply not produced or shipped, the
\$$2.853$ billion penalty is excluded from $Z_{\text{log}}$ (no economic sense).
Under~F, four emergency arcs from S4, S5, S6 (to H2) and S9 (to H2)
are activated at a $\gamma = 2.5$ spot-market premium, restoring full
service at $Z_F = \$8{,}088{,}281$ (S1) and $Z_F = \$8{,}443{,}935$
(S3). Table~\ref{tab:s1s3_unmet} reports the unmet demand per
strategy and product.

\begin{table}[H]
\centering
\caption{Unmet demand (units) under S1 and~S3.}
\label{tab:s1s3_unmet}
\small
\begin{tabular}{llrrr}
\toprule
\textbf{Sc.} & \textbf{Product} & \textbf{R} & \textbf{A} & \textbf{F} \\
\midrule
S1, S3 & B Semiconductors      & 2{,}222 & 2{,}222 & 0 \\
S1, S3 & C Battery comp.        &   631 &   631 & 0 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Cost decomposition under strategy~F --- infeasible scenarios S1 and~S3 (\$).
         Only strategy~F is shown; $Z_R$ and $Z_A$ are not comparable to $Z^*$
         due to unmet demand (see Table~\ref{tab:s1s3_unmet}).}
\label{tab:cost_decomp_s1s3}
\resizebox{\linewidth}{!}{%
\begin{tabular}{lrrr}
\toprule
\textbf{Component} & \textbf{Baseline} & \textbf{S1 (F)} & \textbf{S3 (F)} \\
\midrule
\multicolumn{4}{l}{\textit{Fixed costs}} \\
~~WH opening              & \$22,046 & \$15,915$^\dagger$ & \$15,915$^\dagger$ \\
~~Arc activation          & \$19,638 & \$16,546           & \$18,098           \\
\midrule
\multicolumn{4}{l}{\textit{Variable transport costs --- standard arcs}} \\
~~A (Fertilizers)         & \$638,198 & \$638,046  & \$714,716  \\
~~B (Semiconductors)      & \$2,814,741 & \$1,651,753  & \$1,828,643  \\
~~C (Battery Comp.)       & \$960,176 & \$938,493  & \$1,039,036  \\
\midrule
\multicolumn{4}{l}{\textit{Variable transport costs --- emergency arcs ($\gamma = 2.5$)}} \\
~~B (Semiconductors)      & --- & \$4,202,243 & \$4,202,243 \\
~~C (Battery Comp.)       & --- & \$625,284   & \$625,284   \\
\midrule
\textbf{Total $Z_F$}      & \$4,454,801 & \$8,088,281 & \$8,443,935 \\
\midrule
$\Delta Z_F$ vs $Z^*$     & ---         & \$+3,633,480 & \$+3,989,134 \\
$\Delta Z_F$ (\%)         & ---         & $+81.6\%$    & $+89.6\%$    \\
\bottomrule
\end{tabular}%
}\\[4pt]
\footnotesize
$^\dagger$ W5, W6, W8 closed under greenfield redesign; 11 warehouses remain open
at a combined cost of \$15,915 vs.\ \$22,046 in the baseline.

\end{table}



\paragraph{Interpretation as a conditional lower bound.}
$Z_F(S1) = \$8{,}088{,}281$ should be read as ``the cheapest
network that delivers \emph{all} demand under the closure of~H3,
given that we must reach S4, S5, S6, S9 through a spot-market
emergency arc at a $2.5\times$ premium''. It is the only strategy
that is fully comparable to the baseline because it is the only one
that delivers the same service. The greenfield network closes three
warehouses (W5, W6, W8) and activates three optional arcs, but the
dominant cost driver is the variable transport bill of
\$8{,}055{,}819, nearly twice the baseline equivalent
(\$4{,}413{,}115), driven almost entirely by the emergency arc
procurement for products~B and~C. The closure of~H3 alone therefore
costs $Z_F(S1) - Z^* = \$3{,}633{,}480$ ($+81.6\%$); under~S3
the combination with the T2 energy shock pushes this to $+89.6\%$.
These are the two scenarios for which the baseline simply cannot
continue operating without paying a structural premium.

\subsection{Strategic Assessment}
\label{sec:phase2_strategic}

\paragraph{Most damaging scenario.}
On the comparable $\Delta Z_F$ ledger, S3 dominates everything else
at $+\$3{,}989{,}134$ ($+89.55\%$), with S1 a close second at
$+\$3{,}633{,}480$ ($+81.56\%$). Both are driven by the same
structural cause: the loss of hub~H3 and the forced procurement of
products~B and~C via expensive emergency arcs. S3 adds the T2 modal
shock on top of S1, which raises sea-mode unit costs by $10\%$ along
the very arcs that are most relied upon under the H3 closure, hence
the additional $\$355{,}654$ premium relative to S1 alone. Among
\emph{purely tariff/energy} scenarios, T3 (hub surcharge) is the most
damaging at $+\$852{,}284$ ($+19.13\%$), more than five times the T1
tariff and roughly $1.8\times$ the T2 energy shock. The pattern is
unambiguous: shocks that target the network's \emph{topology}
(H3 closure) are an order of magnitude more dangerous than shocks
that target its \emph{prices}.

\paragraph{Structural weakness of the baseline network.}
Two vulnerabilities recur across the analysis. The first is the
\emph{exclusive dependence on H3} (Singapore) for the
semiconductor supplier cluster (S4 Busan, S5 Taipei, S6 Yokohama)
and for one of the battery-component suppliers (S9 Chengdu): four
out of nine suppliers have only one viable hub of entry, and
losing that hub strands $48.7\%$ of the supply base.
The second is the recurrence of the same handful of adaptation
arcs across multiple disruptions. Under strategy~A, arcs
A188 (W1$\rightarrow$W12, sea) and A224 (W12$\rightarrow$C1, road)
are newly activated under T1, T3, S1 \emph{and}~S3; A317
(W4$\rightarrow$C30, road) appears under T3, S1 and~S3.
These arcs are not specific to any particular shock, they
are the natural relief paths for the baseline whenever it is
perturbed. Their absence from the Phase~1 optimal solution
indicates that the baseline cost-minimisation horizon is slightly
too narrow: a small set of fixed-cost activations would have made
the network materially more robust at very limited expense.

\paragraph{Cost of resilience.}
The ``resilience premium'' for being protected against S1 ex ante is
$Z_F(S1) - Z^* = \$3{,}633{,}480$, or $+81.56\%$ of the baseline. No
realistic preventive investment programme would absorb such a
premium continuously, but the calculation isolates the part of the
disruption cost that is \emph{structural} rather than operational.
Crucially, for all feasible scenarios the greenfield cost $Z_F$ sits
within $0$--$20\%$ of $Z^*$ (T2: $+10.6\%$; T1: $+3.5\%$;
T3: $+19.1\%$; S2: $0\%$), whereas for S1/S3 it explodes to
$+81$--$90\%$. The greenfield benchmark is, in other words,
``close to baseline'' for price shocks and ``far from baseline''
for topology shocks. This dichotomy will guide the Phase~3 design,
which targets the geographic chokepoints, Suez and Panama,
that combine elements of both.

